Global Optimization of an analog method by Means of Genetic Algorithms

### 2016-09-06 Genetic algorithms - MWR/template.tex
Completion of the corrections.

@@

\title{Global Optimization of an Analog Method by Means of Genetic Algorithms}

@@

The document starts by presenting the case study area and the data (section \ref{sec:case_study_data}), the basics of the considered AM variants (section \ref{sec:am}), and the assessed GAs options (section \ref{sec:gas}). The comparative analyses of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:recommendations} and conclusions in section \ref{sec:conclusions}.

@@

Even GAs configurations that will be considered later as inadequate, because they did not reach the global optimum (Fig. \ref{fig:gas_evolution_bad}), did significantly better that the sequential approach. GAs proved promising at optimizing AMs automatically, globally, and objectively.

@@

% TODO: add region name and ref to map
The same experiment was performed for another region, which is sensitive to other meteorological influences (Fig. \ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operator with the predictand. Even though differences can be observed with Fig. \ref{fig:operator_mutation_score_atmlevel}, it is globally the same options that perform better.

@@

After analysis of the most relevant mutation operators, the following advice can be raised (detailed options are provided in section \ref{sec:recommendations}):

@@

\section{Recommended configuration of GAs}
\label{sec:recommendations}

@@

Ref: 95\%   ( 0.2921,  0.3494 )  
Optimized: 95\%   ( 0.3521,  0.4011 )

>>>>

% TODO: check all references to sections
% TODO: reduce font size in plots

@@

\title{Global Optimization of an analog method by Means of Genetic Algorithms}

@@

The document starts by presenting the case study area and the data (section \ref{sec:case_study_data}), the basics of the considered AM variants (section \ref{sec:am}), and the assessed GAs options (section \ref{sec:gas}). The comparative analyses of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:use} and conclusions in section \ref{sec:conclusions}.

@@

Even GAs configurations that will be later rejected, because they did not converge (Fig. \ref{fig:gas_evolution_bad}), did still significantly better that the sequential approach. GAs showed a promising potential at optimizing AMs automatically, globally, and objectively.

@@

The same experiment was performed for another region (Swiss Chablais, see Fig. \ref{fig:map}), which is sensitive to other meteorological influences (Fig. \ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operator with the predictand. Even though differences can be observed with Fig. \ref{fig:operator_mutation_score_atmlevel}, it is globally the same options that perform better.

@@

After analysis of the most relevant mutation operators, the following advice can be raised (detailed options are provided in section \ref{sec:use}.\ref{sec:recommendations}):

@@

\section{Use of GAs ot optimize AMs}
\label{sec:use}

\subsection{Recommended configuration of GAs}
\label{sec:recommendations}

@@

In order to illustrate the gain achievable by the optimization on the considered AM, the Southeast ridges region of the alpine Rhône catchment has been optimized for the whole calibration period (40 years in the 1961-2008 period, leaving out 8 years for validation), instead of the smaller 5-years period.

The optimizer could select the geopotential height at 4 pressure levels, at any time of the day, on unconstrained spatial windows. Moreover, a weighting was introduced in the combination of the criteria processed on each pressure level \citep[such as][]{Horton2012a, Junk2015}. In this case, no new meteorological variable was added, and the method still contains a unique level of analogy.

The performance (CRPSS) of the reference method calibrated by means of the sequential procedure amounts to 32.00\%, with a 0.95 confidence interval (assessed by bootstrapping on 10,000 samples) of (29.21\%; 34.94\%). The method optimized by means of GAs reaches a performance of 37.62\%, with a 0.95 confidence interval of (35.21\%; 40.11\%). The resulting gain is thus statistically significant. The results on all subregions and the physical meaning of the optimized parameters will be discussed in a coming paper.
